\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-30 syntax.tex
Small fix.

A side note: before we dive in more details of our metatheory for linkage (especially the meaning of sealing and $\cC$), we have to mention that, the challenge of incorporating family polymorphism with inductive type mentioned in \ref{chg:extensible-inductive-type} mutates in metatheory because of de Bruijn indices. (Using surface synax), consider the example of a linkage $\{a~:~\bW \sigma; b_1 : a \to T;..\}$ with a bunch of $b_i$ \textit{using} $a$. The tension we need to solve here is between \textit{exhaustiveness checking} and \textit{inheritance (code reuse)}---on one hand, if we want to make sure $b_i$ is pattern matching correctly, then we have to construct $b_i$ term in the context of $\bW\sigma$; on the hand, if we want to let $b_i$ to be inherited into children family with extended inductive type $a~:~\bW \sigma'$, then the old inductive type $a~:~\bW \sigma$ in the context of $b_i$ is stopping that. Our metatheory formulation of linkage is mainly trying to solve this tension.

@@

The reason we need this additional type construct of $\cC\sigma$ here is
to support \textit{code reuse}, as the rule of linkages hinders its
ability to do abstraction. Concretely speaking, (using surface syntax)
we don't have \\ $\goodTerm{\Gamma, \cL(\{a~:~\bW \sigma; b~:~a \to
T\})}{h}{\cL(\{a~:~\cU; b~:~a \to T\})}$\footnote{If we had one,
consider the case $T$ is bottom type and $\sigma$ is empty record and
thus $a$ is initially bottom type. Now the direct projection using \ruleref{Sig Proj} $\goodTerm{\Gamma, a : \cU}{h.b}{a \to \bot}$ will lead to problem because every field in linkage has this implicit universal quantification, and for this case we can substitute $a$ with arbitrary type, say $\top$: $\goodTerm{\Gamma}{h.b[a \mapsto \top]}{\top \to \bot}$ is a contradiction\YZ{You are talking about
overriding here, but you haven't told the reader what overriding means
in your metatheory.}\EDJreply{Ok. I use the projection now instead.}}. This term is important for us to abstract the
concrete inductive type so that the later field can depend on the
abstract interface and achieve \textit{code reuse}. On the other hand,
we do have $\goodTerm{\Gamma, (\Sigma a : \bW\sigma, a \to T)
}{h}{(\Sigma a : \cU, a \to T)}$ because of the rule for existential
(also existential type just don't allow overriding\YZ{Why is it desired that this type in the context does not allow overriding (since it already says 'a : U')?}).
Thus to allow abstraction happens, we need $\cC\sigma$ to compile a
linkage to module as a part of the context and we also need
\ruleref{Lnkg Compile} to specify the compilation from linkage to
module.

@@

This sealing is the general version of the sealed family implemented in the plugin. Our plugin will deduce a sealed ``interface'' for a sealed family using a fixed set of rules but here sealing in metatheory can be arbitrary local morphism. With the definition of sealing judgement in mind, we can see
\ruleref{Sig Add} and \ruleref{Lnkg Add} work exactly as the
implementation. In the implementation, we will have "self__" all around
when defining new fields in our plugin, and this "self__" is exactly the
$A$ in the context of the two fields---especially when we don't do any
sealing, this $A = \cC \sigma$, which is exactly how the implementation
exposes "self__" as a module parameter.

>>>>

A side note: before we dive in more details of our metatheory for linkage (especially the meaning of sealing and $\cC$), we have to mention that, the challenge of incorporating family polymorphism with inductive type mentioned in \ref{chg:extensible-inductive-type} mutates in metatheory because of de Bruijn indices. (Using surface synax), consider the example of a linkage $\{a~:~\bW \sigma; b_1 : a \to T;..\}$ with a bunch of $b_i$ \textit{using} $a$. The tension we need to solve here is between \textit{exhaustiveness checking} and \textit{inheritance (code reuse)}---on one hand, if we want to make sure $b_i$ is pattern matching correctly, then we have to construct $b_i$ term in the context of $a : \bW\sigma$; on the hand, if we want to let $b_i$ to be inherited into children family with extended inductive type $a~:~\bW \sigma'$, then the old inductive type $a~:~\bW \sigma$ in the context of $b_i$ is stopping that and thus we hope $b_i$ constructed in the context of $a : \cU$ (and thus later this $a$ can be compatible with inductive type of any signature). Our metatheory formulation of linkage is mainly trying to solve this tension.

@@

The reason we need this additional type construct of $\cC\sigma$ here is
to support \textit{code reuse}, as the rule of linkages hinders its
ability to do abstraction. Concretely speaking, (using surface syntax)
we don't have \\ $\goodTerm{\Gamma, \cL(\{a~:~\bW \sigma; b~:~a \to
T\})}{h}{\cL(\{a~:~\cU; b~:~a \to T\})}$\footnote{If we had one,
consider the case $T$ is bottom type and $\sigma$ is empty record and
thus $a$ is initially bottom type. Now the direct projection using \ruleref{Sig Proj} $\goodTerm{\Gamma, a : \cU}{h.b}{a \to \bot}$ will lead to problem because every field in linkage has this implicit universal quantification, and for this case we can substitute $a$ with arbitrary type, say $\top$: $\goodTerm{\Gamma}{h.b[a \mapsto \top]}{\top \to \bot}$ is a contradiction\YZ{You are talking about
overriding here, but you haven't told the reader what overriding means
in your metatheory.}\EDJreply{Ok. I use the projection now instead.}}. This term is important for us to abstract the
concrete inductive type so that the later field can depend on the
``abstract interface'' (i.e. $\cL(\{a:\cU~;~b:a \to T\})$) and achieve \textit{code reuse}. \\ On the other hand,
we do have $\goodTerm{\Gamma, (\Sigma a : \bW\sigma, a \to T)
}{h}{(\Sigma a : \cU, a \to T)}$ because of the rule for existential
(also existential type just don't allow overriding\YZ{Why is it desired that this type in the context does not allow overriding (since it already says 'a : U')?}).
Thus to allow abstraction happens, we need $\cC\sigma$ to compile a
linkage to module as a part of the context and we also need
\ruleref{Lnkg Compile} to specify the compilation from linkage to
module.

@@

This sealing is the general version of the sealed family implemented in the plugin. Our plugin will deduce a sealed ``interface'' for a sealed family using a fixed set of rules but here sealing in metatheory can be arbitrary local morphism. With the definition of sealing judgement in mind, we can see
\ruleref{Sig Add} and \ruleref{Lnkg Add} work exactly as the
implementation. In the implementation, we will have "self__" all around
when defining new fields in our plugin, and this "self__" is exactly the
$A$ in the context of the two fields---in our implementation, there is only sealing of inductive type happening (where each inductive type we only know \mintinline{Coq}{T : Set}).
